My title

### 2024-10-21 paper/paper.qmd
intial draft of the data section

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

@@

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

@@

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Pollster

# Idealized Methodology

# References

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Shamalya D
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Data

## Data Set Overview

add a summary statistics table here maybe?

## Variables

Mention any variables that were constructed here, as well

## High Level Data Cleaning

## Summary Statistics

## Graphs for Imp. Variables (relationships)

@@

Public support for political candidates is an essential part of understanding electoral dynamics for a variety of reasons. Public polls provide insights into the preferences and beliefs of certain groups of people, usually voters in specific states or districts, and sometimes to also correlate preferences to demographic information (race, age, neighbourhood, etc).

The results help inform policy decisions, help track the likely outcomes of elections, help government officials and candidates decide where to invest time, funds, and resources to get the desired results. Polling organizations aim to capture data by surveying a representative sample of voters, free from government intervention.

Polling organizations conduct these surveys through various methods. For our particular data set, the following methods have been used to gauge public sentiment:

-   App panel

-   Online panel

-   Email

-   Online ad

-   IVR (interactive voice response)

-   Live phone

-   Text

-   Text-to-web

-   Probability panel

-   Mail-to-phone

Each pollster chooses a method(s) based on what they find to be most convenient, efficient, and providing the best results. Moreover, there are some variables which affect the validity and reliability of the polling results, such as sample size, methodology, population type, etc. Larger samples generally lead to more reliable estimates of public opinion. Some methodologies might be considered more reliable due to certain factors. The pollsters also use different sampling methods (random, stratified, etc) which can affect the validity of the polling results as well.

After collecting the required data, the polling organizations transform these results into more easily comprehensible variables such as numeric grade, poll score, transparency score, and a percentage. These scores are calculated through an extensive process of calculating excess error and bias, adjusting for race difficulty, calculating predictive error and bias, calculating pollster transparency, and combining everything into one single ‘POLLSCORE’, while accounting for luck as well.

Variables such as pollster rating and transparency score help validate the reliability of the pollster and the polling results they publish.

Each entry in the dataset represents a glimpse of public opinion at a specific time and location, capturing measured support percentages alongside contextual variables such as pollster, methodology, and sample size. This extensive approach allows for an enhanced understanding of public support dynamics, facilitating informed analyses of electoral outcomes.

```{r}
library(arrow)
analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))

head(analysis_data)
```
